Supplementary Information

### 2021-08-12 doc/manuscript/ForestGEO_treerings.Rmd
add table footnote
#143

hypotheses_table <- subset(hypotheses_table, select = -c(Q, H, category,notes) )#remove columns that shouldn't be included
ft <- flextable(hypotheses_table)
ft <- italic(ft, i=hypothesis_rows, j=1)
ft <- bold(ft, i=c(question_rows))
ft <- line_spacing(ft, space = 1, part = "all")
ft <- padding(ft, padding.top = 2)
ft <- padding(ft, padding.bottom = 2)
ft <- padding(ft, j = 1, padding.left = 20)
ft <- padding(ft, i = hypothesis_rows, j = 1, padding.left = 10)
ft <- padding(ft, i = question_rows, j = 1, padding.left = 0)
ft <- autofit(ft)
ft <- footnote( ft, i = 1, j = 2,
                value = as_paragraph(c("SSC= species-site combinations")),
                ref_symbols = c("*"),
                part = "header",inline=T)
ft <- footnote( ft, i = 1, j = 1,
                value = as_paragraph(c("Results summarized here are for climate-only models with RW as response variable.")),
                ref_symbols = c("**"),
                part = "body",inline=T)
ft <- footnote( ft, i = c(10,11), j = 2,
                value = as_paragraph(c("Refers to SSC with significant (p<0.05) main effect of climate on RW.")),
                ref_symbols = c("#"),
                part = "body",inline=T)
ft <- footnote( ft, i = 19, j = 1,
                value = as_paragraph(c("Results summarized here are for models with BAI as response variable.")),
                ref_symbols = c("##"),
                part = "body",inline=T)
ft

>>>>

hypotheses_table <- subset(hypotheses_table, select = -c(Q, H, category,notes) )#remove columns that shouldn't be included
ft <- flextable(hypotheses_table)
ft <- italic(ft, i=hypothesis_rows, j=1)
ft <- bold(ft, i=c(question_rows))
ft <- line_spacing(ft, space = 1, part = "all")
ft <- padding(ft, padding.top = 2)
ft <- padding(ft, padding.bottom = 2)
ft <- padding(ft, j = 1, padding.left = 20)
ft <- padding(ft, i = hypothesis_rows, j = 1, padding.left = 10)
ft <- padding(ft, i = question_rows, j = 1, padding.left = 0)
ft <- autofit(ft)
ft <- footnote( ft, i = 1, j = 2,
                value = as_paragraph(c("SSC= species-site combinations")),
                ref_symbols = c("*"),
                part = "header",inline=T)
ft <- footnote( ft, i = 1, j = 1,
                value = as_paragraph(c("Results summarized here are for climate-only models with RW as response variable.")),
                ref_symbols = c("**"),
                part = "body",inline=T)
ft <- footnote( ft, i = c(10,11), j = 2,
                value = as_paragraph(c("Refers to SSC with significant (p<0.05) main effect of climate on RW.")),
                ref_symbols = c("***"),
                part = "body",inline=T)
ft <- footnote( ft, i = 12, j = 1,
                value = as_paragraph(c("Results summarized here are for models without year.")),
                ref_symbols = c("#"),
                part = "body",inline=T)
ft <- footnote( ft, i = 15, j = 2,
                value = as_paragraph(c("100% (9/9 SSC) for models including year")),
                ref_symbols = c("##"),
                part = "body",inline=T)
ft <- footnote( ft, i = 19, j = 1,
                value = as_paragraph(c("Results summarized here are for models with BAI as response variable.")),
                ref_symbols = c("###"),
                part = "body",inline=T)
ft
